A nice acyclic matching on the nerve of the partition lattice

### 2019-11-21 paper3/equivariant.tex
Gerrit fix

By Proposition \ref{eqpatchwork} there exists an $(S_1\times S_{n-1})$-equivariant acyclic matching on ${\cal F}(\Delta(\overline{\Pi}_n))$ such that
\[
\left(\bigcup_{g\in S_1\times S_{n-1}}g\psi[C_{n-1}]\right)\cup\{\alpha_n\}
\]
is the set of critical elements. It is easy to see that this set equals $C_n\cup\{\alpha_n\}$.
\end{proof}
\begin{cor}
\label{moeglichkeit1}
Let $G\subset S_1\times S_{n-1}$ be a subgroup. Then there exists an acyclic matching on ${\cal F}(\Delta(\overline{\Pi}_n))/G$, such that the set of critical simplices consists of the simplices in $C_n/G$ and $\alpha_n/G$.
\end{cor}
\begin{proof}
Apply Remark \ref{quotmatching}.
\end{proof}
\begin{ex}
\label{nicematchingex}
Assume $G=S_1\times S_{n-1}$. The vertices of $\Delta(\overline{\Pi}_n)/S_1\times S_{n-1}$ can be indexed with number partitions of $n$, which we may write as $v_0\oplus v_1+\dots+v_r$, that distinguish the first number, i.e.\ $\oplus$ is non-commutative. The number on the left side of $\oplus$, that is $v_0$, corresponds to the block that contains $1$. There exists an acyclic matching on the poset ${\cal F}(\Delta(\overline{\Pi}_n)/S_1\times S_{n-1})$, where the set of critical simplices consists of the vertex $1\oplus(n-1)$ and the unique simplex $\sigma$ whose vertices are $v_0\oplus 1^{n-v_0}$ with $v_0=2,\dots,n-1$, which has dimension $n-3$.
\end{ex}
A slightly different proof of the result in Example \ref{nicematchingex}, as well as a detailed description of $\Delta(\overline{\Pi}_n)/S_1\times S_{n-1}$, can be found in \cite{donau2}.
\section{Applications}
Let $n\geq 3$ be a fixed natural number.
\begin{cor}
\label{moeglichkeit2}
The topological space $\Delta(\overline{\Pi}_n)$ is $(S_1\times S_{n-1})$-homotopy equivalent to a wedge of $(n-1)!$ spheres of dimension $n-3$. The spheres are indexed with the simplices in $C_n$, which induces an action of $S_1\times S_{n-1}$ on the $(n-1)!$ spheres.
\end{cor}
\begin{proof}
Apply Theorem \ref{freij}.
\end{proof}
\begin{lem}
\label{freetrans}
$S_1\times S_{n-1}$ acts freely and transitively on $C_n$.
\end{lem}
\begin{proof}
Since $C_n=\bigcup_{g\in S_1\times S_{n-1}}g\psi[C_{n-1}]$, the action is transitive, which follows inductively by the second statement of Proposition \ref{eqpatchwork}.

>>>>

By Proposition \ref{eqpatchwork} there exists an $(S_1\times S_{n-1})$-equivariant acyclic matching on ${\cal F}(\Delta(\overline{\Pi}_n))$ such that
\[
\left(\bigcup_{g\in S_1\times S_{n-1}}g\psi[C_{n-1}]\right)\cup\{\alpha_n\}
\]
is the set of critical elements. It is easy to see that this set equals $C_n\cup\{\alpha_n\}$.
\end{proof}
\begin{cor}
\label{moeglichkeit1}
Let $G\subset S_1\times S_{n-1}$ be a subgroup. Then there exists an acyclic matching on ${\cal F}(\Delta(\overline{\Pi}_n))/G$, such that the set of critical simplices consists of the simplices in $C_n/G$ and $\alpha_n/G$.
\end{cor}
\begin{proof}
Apply Remark \ref{quotmatching}.
\end{proof}
\begin{ex}
\label{nicematchingex}
Assume $G=S_1\times S_{n-1}$. The vertices of $\Delta(\overline{\Pi}_n)/S_1\times S_{n-1}$ can be indexed with number partitions of $n$, which we may write as $v_0\oplus v_1+\dots+v_r$, that distinguish the first number, i.e.\ $\oplus$ is non-commutative. The number on the left side of $\oplus$, that is $v_0$, corresponds to the block that contains $1$. There exists an acyclic matching on the poset ${\cal F}(\Delta(\overline{\Pi}_n)/S_1\times S_{n-1})$, where the set of critical simplices consists of the vertex $1\oplus(n-1)$ and the simplex $\sigma$ of dimension $n-3$ whose vertices are $v_0\oplus 1^{n-v_0}$ with $v_0=2,\dots,n-1$.
\end{ex}
A slightly different proof of the result in Example \ref{nicematchingex}, as well as a detailed description of $\Delta(\overline{\Pi}_n)/S_1\times S_{n-1}$, can be found in \cite{donau2}.
\section{Applications}
Let $n\geq 3$ be a fixed natural number.
\begin{cor}
\label{moeglichkeit2}
The topological space $\Delta(\overline{\Pi}_n)$ is $(S_1\times S_{n-1})$-homotopy equivalent to a wedge of $(n-1)!$ spheres of dimension $n-3$. The spheres are indexed with the simplices in $C_n$, which induces an action of $S_1\times S_{n-1}$ on the $(n-1)!$ spheres.
\end{cor}
\begin{proof}
Apply Theorem \ref{freij}.
\end{proof}
\begin{lem}
\label{freetrans}
$S_1\times S_{n-1}$ acts freely and transitively on $C_n$.
\end{lem}
\begin{proof}
Since $C_n=\bigcup_{g\in S_1\times S_{n-1}}g\psi[C_{n-1}]$, the action is transitive, which follows inductively by the second statement of Proposition \ref{eqpatchwork}.
